%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.11 (19/6/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Bigani} % Your first name
\familyname{Sehurutshi} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Curriculum Vitae}
\address{P.O Box 70625}{Gaborone, Botswana}
\mobile{(267) 74591855}
\phone{(267) 3554887}
\fax{(267) 355 4194}
\email {sehurub@gmail.com}
%\homepage{staff.org.edu/~jsmith}{staff.org.edu/$\sim$jsmith} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
%\extrainfo{additional information}
%\photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{ }

%----------------------------------------------------------------------------------------

\begin{document}
\label{Summary}

\makecvtitle % Print the CV title
%----------------------------------------------------------------------------------------

% SUMMARY SECTION
%-------------------------------------------------------------
%--------------------------------------------------------------------

%	RESEARCH SECTION
%--------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------

%	WORK EXPERIENCE SECTION
%-------------------------------------------------------------

\section{Professional Experience}

%\subsection{Vocational}
\cventry{April 2010--Present}{HPC System Administrator}{\textsc{Department of Computer Science }}{University of Botswana}{}{
\newline{}\newline{}
\begin{itemize}{
\item Install, configure, upgrade, troubleshoot and administration of Web servers, Databases and Linux and Windows servers.
\item Install,configure and troubleshoot Linux Servers and Desktops.
\item Linux Server Administration(Virtualization, NFS, DHCP, LDAP, Reverse proxy, FTP,SSH, VPN and LVM).
\item Orchestrated containerized applications using Docker and Kubernetes, ensuring efficient resource utilization and scalability.
\item Excellent knowledge in designing, prototyping and deploying HPC clusters.
\item Installing and supporting parallel computing environments (e.g. OpenMPI, MVAPICH, etc.)
\item Create, maintain and implement scripts in order to reduce administrative efforts. 
\item Infrastructure procurement, management and maintenance.
\item Configure and administer Databases, Networks and Web-servers used for teaching. Web standards (HTTP, JSON, RESTful APIs).
\item Tech lead in Cloud Computing Solutions (RDS, DynamoDB,and Aurora, EC2, Beanstalk, EKS and Lambda, Amazon S3, EBS and EFS).
\item Experience administering, configuring, and supporting HPC clusters, including systems with accelerators, and high performance file systems and storage. This includes hardware installation, configuration, upgrades and repairs.
\item Scientific Computing Application deployment and support (WRF,Ansys AnyBLAST, TOMO3D, R, MATLAB, QGIS, Gaussian,jif3D, Spades and many more.)
\item Train and support Students, Staff  on Linux and AWS Cloud courses. 
\item Marketing, budgeting,creative teaching, train Instructors and extensive outreach programs for the Linux and AWS Academy.
\end{itemize}}}

%------------------------------------------------

%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2015}{Masters of Science Computer Information Systems}{The University of Botswana}{Gaborone}{\textit{Botswana}}{}  % Arguments not required can be left empty
\cventry{2009}{Bachelor of Information Systems(Computer Information Systems)}{The University of Botswana}{Gaborone}{\textit{Botswana}}{}

%----------------------------------------------------------------------------------------

%	CERTIFICATION SECTION
%-------------------------------------------------------------

\section{Certifications}
\cvitem{2023}{AWS Certified Solutions Architect- Associate}
\cvitem{2023}{LPI Security Essentials}
\cvitem{2022}{Linux Foundation Devops and SRE Fundamentals}
\cvitem{2021}{Microsoft Certified Azure Fundamentals }
\cvitem{2021}{AWS Certified Cloud Practitioner}
\cvitem{2020}{LPIC-1 LINUX Administrator(LPI) }
\cvitem{2016}{COBIT 5 FOUNDATION (2016)}
\cvitem{2014}{ITIL Foundation Certificate In IT Service Management}
\cvitem{2013}{SAP ERP4school Foundation}

%-------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%-------------------------------------------------------------

\section{Computer skills}

\cvitem{Programming}{\textsc{java}, {Python}, {HTML}, {Perl},{Ruby}, {PHP} and {Bash scripting}}
\cvitem{Databases}{\textsc{MYSQL}, MARIADB, POSTGRESQL, ORACLE, RDS and DYNAMODB}
\cvitem {Webserver}{\textsc{APACHE}, NGINX, TOMCAT}
\cvitem{Utilities/Tools}{SAMBA, OPENHPC, KICKSTART, REMMINA, Nmap, Openvas, openssh, Wireshark, Packet Tracer, GNS3, backtrack, security onion and putty.}
\cvitem{Version Control systems}{GIT and GITLAB}
\cvitem{CI/CD Tools}{Jenkins and Gitlab CI}
\cvitem{Monitoring Tools}{Nagios, Grafana  and Ganglia}
\cvitem{Cloud Platforms}{\textsc{AWS}, Microsoft AZURE, Google Cloud Platform (GCP) and OPENSTACK}
\cvitem{Networking}{Routing Protocols, IP Addressing, TCP/IP, VLANS, Network Security, DNS.DHCP, VPC, Load Balancers}
\cvitem{Security}{IAM, Security Groups, NEtwork ACL Policies and roles.}
\cvitem{Virtualization}{Virtualbox,Xenserver and VMWARE}
\cvitem{Infrastructure as Code}{Cloudformation, Terraform}
\cvitem{Containers and Orchestration}{LXC, LXD, Docker, Podman, FreeBSD Jails, Openshift and Kubernetes}
\cvitem{Configuration Management}{Ansible, Puppet, Cobbler}

%----------------------------------------------------------------------------------------
%	PROJECTS
%-------------------------------------------------------------


%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

%PROFESSIONAL MEMBERSHIP SECTION
%------------------------------------------------------------------------------

\section{Professional Membership}

\cvitem{}{A member of Institute of Information Technology Professionals South Africa, membership no: S043688}
\cvitem{}{ A member of the Linux Professional Institute, LPI ID: LPI000297068}


%----------------------------------------------------------------------------------------
\section{References}
\cvitem{}{Available Upon Request}






%----------------------------------------------------------------------------------------


\end{document}
